Races with hyper3 objects

### 2022-06-20 inst/race3.Rmd
slight typos

(takes about an hour to process)

@@

as a standard support function which has a maximum value of zero when
evaluated at $\hat{a]=\sqrt{2}-1$.  For example, we can test the null
that $a=b=\frac{1}{2}$, the statement that the competitors have equal
Bradley-Terry strengths:

@@

The $p$-value is about 0.81, exceeding 0.05; thus we have no strong
evidence to reject the null of $a=\frac{1}{2}.

Further, we can use either analytical or numerical methods to find a
credible interval.  With an $n$-unit of support criterion the
analytical solution to $\mathcal{S}(p)=-2$ is given by defining
$X=\log(3-2\sqrt{2})-n$ and solving $p(1-p)/(1+p)=X$, or
$p_\pm=\left(1-X\pm\sqrt{1+4X+X^2}\right)/2$, the two roots being the
lower and upper limits of the credible interval.  Graphically:

>>>>

(takes about an hour to process without cache)

<p style="text-align: right;">
![](`r system.file("help/figures/hyper2.png", package = "hyper2")`){width=10%}
</p>

@@

as a standard support function which has a maximum value of zero when
evaluated at $\hat{a}=\sqrt{2}-1$.  For example, we can test the null
that $a=b=\frac{1}{2}$, the statement that the competitors have equal
Bradley-Terry strengths:

@@

The $p$-value is about 0.81, exceeding 0.05; thus we have no strong
evidence to reject the null of $a=\frac{1}{2}$.  Further, we can use
either analytical or numerical methods to find a credible interval.
With an $n$-unit of support criterion the analytical solution to
$\mathcal{S}(p)=-2$ is given by defining $X=\log(3-2\sqrt{2})-n$ and
solving $p(1-p)/(1+p)=X$, or
$p_\pm=\left(1-X\pm\sqrt{1+4X+X^2}\right)/2$, the two roots being the
lower and upper limits of the credible interval.  Graphically:
